Certified Knowledge Compilation \\ with Application to Formally Verified Model Counting

### 2023-08-20 doc/JAIR/jair-paper.tex
More progress

We have developed an online supplement to this
paper~\cite{bryant:sat:2023:supplement} that includes
a worked example, more details on the algorithms,
and extensive experimental results.

>>>>

This paper is an extended version of one published at the
2023 Conference on the Theory and Application of Boolean Satisfiability~\cite{bryant:sat:2023}.
